Sound Similarity, Sound Matching, and Differentiable Audio Synthesizer Control

### 2025-04-24 main.tex
Updates from Overleaf

\section{Weaknesses}
% synthesizer simplicity
% arbitrary parameter selection
Compared to previous work, we presented a relatively more cohesive approach to iterative sound-matching which utilizes and compares four loss functions and four synthesis methods. However, there are many other untested methods of synthesis that can be combined in practically infinite ways.

>>>>

\section{Weaknesses}
Compared to previous work, we presented a relatively more cohesive approach to iterative sound-matching which utilizes and compares four loss functions and four synthesis methods. However, there are many other untested methods of synthesis that can be combined in practically infinite ways.
